When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-09-01 06_Paper/COG-ED/Stage 2/Manuscript.tex
included acknowledgement and fixed 3 digit format

\linenumbers
\usepackage{csquotes}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{setspace}\doublespacing
\usepackage[final]{pdfpages}
\usepackage{chngcntr}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={When easy is not preferred: A discounting paradigm to assess load-independent task preference},
  pdfauthor={Josephine Zerna,1, Christoph Scheffel,1, Corinna Kührt1, \& Alexander Strobel1},
  pdflang={en-EN},
  pdfkeywords={effort discounting, registered report, specification curve analysis, need for cognition, \(n\)-back},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Psychology, Technische Universität Dresden, 01062 Dresden, Germany}

@@

There were two necessary adjustments of the methods.
First, we failed to update the necessary sample size after the analyses changed with the first review round.
Instead of the 72 subjects stated above, the largest minimum sample size was actually 53 subjects (see hypothesis 1b in the Design Table in the Supplementary Material).
And secondly, we changed to which hypothesis we applied the specification curve analysis (SCA).
In the initial Stage 1 submission, we had applied it to the MLM of hypothesis 2b, which at this point included NFC as a predictor.
Following the advice of the reviewers, we removed NFC from the MLM, and analyzed NFC in an rmANOVA (hypothesis 3a) instead.
Since NFC was of great interest to us, we decided to apply the SCA to hypothesis 3a rather than 2b to provide a measure of robustness.
However, hypothesis 3a does not contain any RT data, so the SCA is only useful for the MLM in hypothesis 2b.
Therefore, we applied it to the MLM.

@@

We used rmANOVAs to investigate whether objective performance measures and subjective task load measures changed across \(n\)-back levels.
For each rmANOVA we report the generalized eta squared \(\hat{\eta}^2_G\), which estimates the effect size in analyses that contain both manipulated and non-manipulated terms.
The performance measure \(d'\) did not change across \(n\)-back levels (\(F(2.85, 327.28) = 0.01\), \(p = .999\), \(\hat{\eta}^2_G = .000\), 90\% CI \([.000, .000]\), \(\mathrm{BF}_{\textrm{10}} = 3.31 \times 10^{-3}\)), but the median RT did (\(F(2.46, 283.05) = 98.67\), \(p < .001\), \(\hat{\eta}^2_G = .192\), 90\% CI \([.130, .248]\), \(\mathrm{BF}_{\textrm{10}} = 2.28 \times 10^{34}\)), evidence was not in favour of H1a but in favour of H1b.
Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
It did not differ between 2- and 4-back, and it was higher for 3- than for 4-back (Table~\ref{tab:H1b-contrasts}).

@@

When asking participants what motivated their decisions in the cognitive effort discounting paradigm, 11.2\% stated that they wanted to avoid boredom, 22.4\% stated that they wanted a challenge, 34.5\% stated that they wanted to avoid effort, and 4.3\% stated that they wanted to relax.
The remaining 27.6\% of participants used the free text field and provided reasons such as ``I wanted a fair relation of effort and reward.'', ``I wanted the fun that I had in the more challenging levels.'', ``I wanted to maximize reward first and minimize effort second.'', or ``I did not want to perform poorly when I was being paid for it.''.
Figure S.1 in the Supplementary Material shows the different motivations in the context of the SVs per \(n\)-back level.

@@

The declining logistic contrast had the highest effect estimate (\(t(345) = 12.97\), \(p < .001\)), suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.

Consequently, we had to adapt the MLM to incorporate this non-linear trend.
To apply the contrast to the \(n\)-back levels, we had to turn the variables into a factor, with two consequences:
Centered variables cannot be turned into factors, so we entered the variable level in its raw form, and factors cannot be used as random slopes, so the model is now defined as:
\[
SV \sim level\ + d' + median RT + (1|subject)
\]
This means that the intercept still varied between subjects, but there were no random slopes anymore.
To provide more than one observation per factor level, we used the two rounds per \(n\)-back level per subject, rather than \(n\)-back levels per subject.
The ICC of the null model indicated that there was a correlation of \(r=\) .096 between the SVs of a subject, i.e.~that 9.59\% of variance in SVs could be explained by differences between participants.
We did not use an optimization algorithm to improve the fit of the random intercept model.
A total of 9 data points from 6 participants were excluded, because the residuals exceeded 3 SD above the mean.
The results of the final model are displayed in Table~\ref{tab:H2b-results}.

@@

\begin{tabular}{llllllll}
\toprule
Parameter & \multicolumn{1}{c}{Beta} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$-value} & \multicolumn{1}{c}{$p$-value} & \multicolumn{1}{c}{$f^{2}$} & \multicolumn{1}{c}{Random Effects (SD)}\\
\midrule
Intercept & 0.81 & 0.01 & 114.82 & 78.34 & <.001 &  & 0.09\\
n-back level & 0.05 & 0.00 & 799.38 & 18.22 & <.001 & 0.64 & \\
d' & 0.02 & 0.00 & 798.75 & 5.60 & <.001 & 0.04 & \\
median RT & 0.02 & 0.07 & 798.58 & 0.30 & 0.768 & 0.00 & \\
\bottomrule
\addlinespace
\end{tabular}

@@

An exploratory ANOVA was used to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other (\(\chi^2 (2)\) = 34.48, \(p<.001\)), and with an Akaike Information Criterion of \(AIC=-492.61\) and a Bayesian Information Criterion of \(BIC=-454.02\) the declining logistic model was superior to the linear model (\(AIC=-462.12\), \(BIC=-433.18\)).
Both AIC and BIC subtract the likelihood of the model from the number of parameters and/or data points, so lower values indicate better model fit.
The final model had an effect size of \(f^{2}=\) 0.64 for the \(n\)-back levels and \(f^{2}=\) 0.04 for \(d'\), which are considered large and small, respectively\textsuperscript{46}.
This means that the \(n\)-back level explained 64.20\% and \(d'\) explained 3.95\% of variance in SVs relative to the unexplained variance, respectively.
The beta coefficient indicated that with every 1-unit increase in \(d'\), the SV increased by 0.02.
Due to the coding scheme of the logistic contrast, the beta coefficient of the \(n\)-back level has to be interpreted inversely, so SVs decline with increasing \(n\)-back level.
The effect size of the median RT was \(f^{2}=\) 0.00.
Since SVs decline with increasing level, beyond the variance explained by \(d'\), evidence was in favour of H2b.

@@

Regardless of the preprocessing pipeline, \(n\)-back level and \(d'\) were significant predictors of SVs, and had stable effect estimates across all pipelines.
There was only one pipeline in which the median RT was a significant predictor of SVs.
This pipeline contained data that had been inverse transformed across subjects but within conditions, i.e.~within the round of an \(n\)-back level, and RTs beyond 2 \(MAD\) from the median had been excluded.

@@

Figure~\ref{fig:nfcgroups-sv} shows the SVs per \(n\)-back level for participants with NFC scores above and below the median.
There is a concentration of participants who have assigned their highest SV to 1-back, and this concentration fades across \(n\)-back levels.
At the same time, there is a subtle separation of SVs across \(n\)-back levels, depending on the participant's NFC score: While the SVs of those with higher NFC scores remain elevated, the SVs of those with lower NFC scores decline more strongly.
Specifically, \(n=71\) participants had an absolute preference for 1-back, \(n=18\) for 2-back, \(n=9\) for 3-back, and \(n=13\) for 4-back.
There were \(n=5\) participants who did not have an absolute preference for any \(n\)-back level, i.e.~none of their SVs was 1.

{[}FIGURE \ref{fig:nfcgroups-sv} HERE{]}

The median NFC was 16, with \(n=57\) subjects below and \(n=59\) above the median.
We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of the \(n\)-back level (\(F(1, 114) = 9.13\), \(p = .003\), \(\hat{\eta}^2_G = .040\), 90\% CI \([.002, .115]\), \(\mathrm{BF}_{\textrm{10}} = 12.68\)), but neither a main effect of the NFC group (\(F(1, 114) = 3.18\), \(p = .077\), \(\hat{\eta}^2_G = .013\), 90\% CI \([.000, .068]\), \(\mathrm{BF}_{\textrm{10}} = 0.56\)) nor an interaction of NFC group and \(n\)-back level (\(F(1, 114) = 0.46\), \(p = .499\), \(\hat{\eta}^2_G = .002\), 90\% CI \([.000, .037]\)), so evidence was not in favour of H3a.
Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (\(t(114) = -3.02\), \(p = .003\)), but there were large inter-individual differences (Figure~\ref{fig:h3ac-plot}a).
This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, again resembling the declining logistic function.

{[}FIGURE \ref{fig:h3ac-plot} HERE{]}

The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of \(n\)-back level (\(F(2.10, 239.56) = 154.50\), \(p < .001\), \(\hat{\eta}^2_G = .223\), 90\% CI \([.159, .282]\), \(\mathrm{BF}_{\textrm{10}} = 2.22 \times 10^{45}\)) and an interaction between \(n\)-back level and NFC scores (\(F(2.10, 239.56) = 4.93\), \(p = .007\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .025]\)), but no main effect of NFC scores (\(F(1, 114) = 3.22\), \(p = .075\), \(\hat{\eta}^2_G = .022\), 90\% CI \([.000, .084]\), \(\mathrm{BF}_{\textrm{10}} = 1.75 \times 10^{2}\)).
Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (\(t(114) = -2.15\), \(p = .033\), \(\mathrm{BF}_{\textrm{10}} = 11.15\)) and for 4-back (\(t(114) = -2.89\), \(p = .005\), \(\mathrm{BF}_{\textrm{10}} = 336.88\)) than those with NFC scores above the median, so evidence was in favour of H3b.
Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of \(n\)-back levels (Figure~\ref{fig:h3b-plot}).

{[}FIGURE \ref{fig:h3b-plot} HERE{]}

With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of NFC group (\(F(1, 114) = 8.43\), \(p = .004\), \(\hat{\eta}^2_G = .043\), 90\% CI \([.003, .119]\), \(\mathrm{BF}_{\textrm{10}} = 14.26\)) and a main effect of the \(n\)-back level (\(F(1, 114) = 10.21\), \(p = .002\), \(\hat{\eta}^2_G = .034\), 90\% CI \([.000, .105]\), ), but no interaction (\(F(1, 114) = 2.59\), \(p = .110\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .058]\)).
In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (\(t(114) = 2.90\), \(p = .004\)) (Figure~\ref{fig:h3ac-plot}b).
Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was more negative than that of 1- and 2-back (\(t(114) = 3.20\), \(p = .002\)), indicating that in the same way in which the SVs decreased more strongly from 2- to 3-back than from 1- to 2-back, the aversion increased more strongly.
The full results of these analyses of NFC group differences can be found in Table S.11 to S.15 in the Supplementary Material.

\hypertarget{exploratory-analysis}{%
\section{Exploratory analysis}\label{exploratory-analysis}}

To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher \(n\)-back levels, we computed an rmANOVA with the within-factor level (1 to 4) and the between-factor NFC group (below/above median).
There was no main effect of NFC group (\(F(1, 114) = 2.63\), \(p = .108\), \(\hat{\eta}^2_G = .007\), 90\% CI \([.000, .053]\), \(2.95 \times 10^{-1}\)), but a main effect of the \(n\)-back level (\(F(2.01, 229.39) = 67.39\), \(p < .001\), \(\hat{\eta}^2_G = .295\), 90\% CI \([.228, .354]\), \(2.70 \times 10^{30}\)) and an interaction (\(F(2.01, 229.39) = 3.24\), \(p = .041\), \(\hat{\eta}^2_G = .020\), 90\% CI \([.000, .044]\)).
Post-hoc tests for the main effect of level showed that SVs were lower for the more difficult \(n\)-back level in each paired contrast except for 1- versus 2-back.
Post-hoc tests for the interaction effect showed that the NFC groups only had a significant difference in SVs for 4-back, where participants below the NFC median had lower scores (\(\Delta M = 0.11\), 95\% CI \([0.01, 0.22]\), \(t(114) = 2.13\), \(p = .036\)).
Despite not reaching significance, 1-back was the only level in which participants with NFC scores above the median seemed to have lower SVs than those with scores below the median (\(\Delta M = -0.05\), 95\% CI \([-0.11, 0.01]\), \(t(114) = -1.50\), \(p = .136\)).
The full results of this exploratory analysis of NFC group differences can be found in Table S.16 and S.17 in the Supplementary Material.

@@

The performance measure \(d'\) did not differ across \(n\)-back levels, but the RT increased from 1- to 2- to 3-back and then remained on a high level for 4-back.
This points to three important characteristics of the \(n\)-back task in this context.
Firstly, RT as a valid group-level indicator of performance might only be useful for levels up to \(n=3\), and could be used to investigate inter-individual differences for \(n>3\).
Secondly, there is a speed-accuracy tradeoff in the first three levels, that might even re-emerge in higher levels, where \(d'\) would decline and RT would remain stable.
And lastly, the fact that neither accuracy nor speed is an informative performance measure by itself has been observed before\textsuperscript{47} and both show different associations with various measures of intelligence\textsuperscript{4}, suggesting that they should always be reported as separate indices.
Additionally, \(d'\) might not have differed across \(n\)-back levels because the manipulation of task load is not strictly continuous.
Several participants said that they perceived 3-back as more difficult than 4-back because they found it is easier to remember chunks of stimuli when \(n\) was an even number than when \(n\) was an odd number.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Thomson2022}{}}%
\CSLLeftMargin{48. }%
\CSLRightInline{Thomson, K. S. \& Oppenheimer, D. M. \href{https://doi.org/10.1177/17456916211064896}{The {``}{E}ffort {E}lephant{''} in the room: {W}hat is effort, anyway?} \emph{Perspectives on Psychological Science} \textbf{17}, 1633--1652 (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-KleinFluegge2015}{}}%
\CSLLeftMargin{49. }%
\CSLRightInline{Klein-Flügge, M. C., Kennerley, S. W., Saraiva, A. C., Penny, W. D. \& Bestmann, S. \href{https://doi.org/10.1371/journal.pcbi.1004116}{Behavioral modeling of human choices reveals dissociable effects of physical effort and temporal delay on reward devaluation}. \emph{{PLOS} Computational Biology} \textbf{11}, e1004116 (2015).}

>>>>

\linenumbers
\usepackage{csquotes}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{setspace}\doublespacing
\usepackage[final]{pdfpages}
\usepackage{chngcntr}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={When easy is not preferred: A discounting paradigm to assess load-independent task preference},
  pdfauthor={Josephine Zerna,1, Christoph Scheffel,1, Corinna Kührt1, \& Alexander Strobel1},
  pdflang={en-EN},
  pdfkeywords={effort discounting, registered report, specification curve analysis, need for cognition, \(n\)-back},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Psychology, Dresden University of Technology, 01062 Dresden, Germany}

@@

There were three necessary adjustments of the methods.
First, we failed to update the necessary sample size after the analyses changed with the first review round.
Instead of the 72 subjects stated above, the largest minimum sample size was actually 53 subjects (see hypothesis 1b in the Design Table in the Supplementary Material).
Secondly, we changed to which hypothesis we applied the specification curve analysis (SCA).
In the initial Stage 1 submission, we had applied it to the MLM of hypothesis 2b, which at this point included NFC as a predictor.
Following the advice of the reviewers, we removed NFC from the MLM, and analyzed NFC in an rmANOVA (hypothesis 3a) instead.
Since NFC was of great interest to us, we decided to apply the SCA to hypothesis 3a rather than 2b to provide a measure of robustness.
However, hypothesis 3a does not contain any RT data, so the SCA is only useful for the MLM in hypothesis 2b.
Therefore, we applied it to the MLM.
The final adjustment was made during the Stage 2 revision.
A fellow researcher made us aware that by using the z-transformed hit and false alarm rates for the computation of \(d'\), the mean of \(d'\) would be approximately 0 for each \(n\)-back level by design.
Consequently, \(d'\) could not show changes across \(n\)-back levels in the manipulation check and would likely yield different results in the MLM.
Therefore, we computed \(d'\) with unstandardized hit and false alarm rates.
We would like to thank Georgia Clay for pointing us to this fallacy.

@@

We used rmANOVAs to investigate whether objective performance measures and subjective task load measures changed across \(n\)-back levels.
For each rmANOVA we report the generalized eta squared \(\hat{\eta}^2_G\), which estimates the effect size in analyses that contain both manipulated and non-manipulated terms.
In line with hypothesis H1a, the performance measure \(d'\) decreased across \(n\)-back levels (\(F(2.74, 315.51) = 197.18\), \(p < .001\), \(\hat{\eta}^2_G = .464\), 90\% CI \([.403, .516]\), \(\mathrm{BF}_{\textrm{10}} = 1.56 \times 10^{101}\)).
It decreased more strongly from 2- to 3-back (\(t(345) = 10.41\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.71 \times 10^{23}\)) than from 1- to 2-back (\(t(345) = 4.31\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 93,954.04\)) or 3- to 4-back (\(t(345) = 7.18\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 2.45 \times 10^{14}\)).
Similarly, the median RT increased across \(n\)-back levels (\(F(2.46, 283.05) = 98.67\), \(p < .001\), \(\hat{\eta}^2_G = .192\), 90\% CI \([.130, .248]\), \(\mathrm{BF}_{\textrm{10}} = 2.28 \times 10^{34}\)), supporting hypothesis H1b.
Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
It did not differ between 2- and 4-back, and it was higher for 3- than for 4-back (Table~\ref{tab:H1b-contrasts}).

@@

The different curves of SVs across \(n\)-back levels can be seen in Figure~\ref{fig:sv-by-pref}, grouped into those participants who had an SV of 1.0 for 1-back (\(n=71\)), for 2-back (\(n=18\)), for 3-back (\(n=9\)), for 4-back (\(n=13\)), or all SVs below 1.0, i.e.~no absolute preference for any level (\(n=5\)).
While the majority of participants preferred the easiest level and showed an approximately linear decline of SVs with increasing task-load, a substantial part of the sample had higher SVs for one of the more difficult \(n\)-back levels.
However, each panel in Figure~\ref{fig:sv-by-pref} contains curves of participants who had large differences between their four SVs and curves of participants who had a difference of less than 0.2 between their highest and their lowest SV, so preferring one level does not necessarily mean having a strong aversion against the others, regardless of difficulty level.

{[}FIGURE \ref{fig:sv-by-pref} HERE{]}

When asking participants what motivated their decisions in the cognitive effort discounting paradigm, 11.2\% stated that they wanted to avoid boredom, 22.4\% stated that they wanted a challenge, 34.5\% stated that they wanted to avoid effort, and 4.3\% stated that they wanted to relax.
The remaining 27.6\% of participants used the free text field and provided reasons such as ``I wanted a fair relation of effort and reward.'', ``I wanted the fun that I had in the more challenging levels.'', ``I wanted to maximize reward first and minimize effort second.'', or ``I did not want to perform poorly when I was being paid for it.''.
Figure \ref{fig:motivation} shows the different motivations in the context of the SVs per \(n\)-back level.

{[}FIGURE \ref{fig:motivation} HERE{]}

@@

The declining logistic contrast had the highest effect estimate (\(t(345) = 12.97\), \(p < .001\)), suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.
Based on the effect estimate, the ascending quadratic and the skewed normal contrasts were rejected in favour of the declining logistic contrast.

Consequently, we had to adapt the MLM to incorporate this non-linear trend.
To apply the contrast to the \(n\)-back levels, we had to turn the variables into a factor, with two consequences:
Centered variables cannot be turned into factors, so we entered the variable level in its raw form, and factors cannot be used as random slopes, so the model is now defined as:
\[
SV \sim level\ + d' + median RT + (1|subject)
\]
This means that the intercept still varied between subjects, but there were no random slopes anymore.
To provide more than one observation per factor level, we used the two rounds per \(n\)-back level per subject, rather than \(n\)-back levels per subject.
The ICC of the null model indicated that there was a correlation of \(r=\) .096 between the SVs of a subject, i.e.~that 9.59\% of variance in SVs could be explained by differences between participants.
We did not use an optimization algorithm to improve the fit of the random intercept model.
A total of 10 data points from 6 participants were excluded, because the residuals exceeded 3 SD above the mean.
The results of the final model are displayed in Table~\ref{tab:H2b-results}.

@@

\begin{tabular}{llllllll}
\toprule
Parameter & \multicolumn{1}{c}{Beta} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$-value} & \multicolumn{1}{c}{$p$-value} & \multicolumn{1}{c}{$f^{2}$} & \multicolumn{1}{c}{Random Effects (SD)}\\
\midrule
Intercept & 0.81 & 0.01 & 115.00 & 78.68 & <.001 &  & 0.09\\
n-back level & 0.03 & 0.00 & 797.54 & 9.99 & <.001 & 0.21 & \\
d' & 0.21 & 0.03 & 797.63 & 6.28 & <.001 & 0.05 & \\
median RT & 0.03 & 0.07 & 797.80 & 0.42 & 0.674 & 0.00 & \\
\bottomrule
\addlinespace
\end{tabular}

@@

An exploratory ANOVA was used to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other (\(\chi^2 (2)\) = 28.35, \(p<.001\)), and with an Akaike Information Criterion of \(AIC=-510.93\) and a Bayesian Information Criterion of \(BIC=-472.35\) the declining logistic model was superior to the linear model (\(AIC=-486.58\), \(BIC=-457.65\)).
Both AIC and BIC subtract the likelihood of the model from the number of parameters and/or data points, so lower values indicate better model fit.
The final model had an effect size of \(f^{2}=\) 0.21 for the \(n\)-back levels and \(f^{2}=\) 0.05 for \(d'\), which are considered medium and small, respectively\textsuperscript{46}.
This means that the \(n\)-back level explained 20.67\% and \(d'\) explained 4.90\% of variance in SVs relative to the unexplained variance, respectively.
The beta coefficient indicated that with every 1-unit increase in \(d'\), the SV increased by 0.21.
Due to the coding scheme of the logistic contrast, the beta coefficient of the \(n\)-back level has to be interpreted inversely, so SVs decline with increasing \(n\)-back level.
The effect size of the median RT was \(f^{2}=\) 0.00.
Since SVs decline with increasing level, beyond the variance explained by \(d'\), evidence was in favour of H2b.

@@

Regardless of the preprocessing pipeline, \(n\)-back level and \(d'\) were significant predictors of SVs, and had stable effect estimates across all pipelines.
There was no pipeline in which the median RT was a significant predictor of SVs, but it showed volatile effect estimates across pipelines.
The pipelines that yielded the highest estimates for \(d'\) and the median RT used log-transformed data, irrespective of the dimension and exclusion criteria.

@@

The median NFC was 16, with \(n=57\) subjects below and \(n=59\) above the median.
We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of the \(n\)-back level (\(F(1, 114) = 9.13\), \(p = .003\), \(\hat{\eta}^2_G = .040\), 90\% CI \([.002, .115]\), \(\mathrm{BF}_{\textrm{10}} = 12.68 \pm 0.00\%\)), but neither a main effect of the NFC group (\(F(1, 114) = 3.18\), \(p = .077\), \(\hat{\eta}^2_G = .013\), 90\% CI \([.000, .068]\), \(\mathrm{BF}_{\textrm{10}} = 0.56 \pm 0.03\%\)) nor an interaction of NFC group and \(n\)-back level (\(F(1, 114) = 0.46\), \(p = .499\), \(\hat{\eta}^2_G = .002\), 90\% CI \([.000, .037]\)), so evidence was not in favour of H3a.
Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (\(t(114) = -3.02\), \(p = .003\)), but there were large inter-individual differences (Supplementary Figure S2a).
This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, again resembling the declining logistic function.

The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of \(n\)-back level (\(F(2.10, 239.56) = 154.50\), \(p < .001\), \(\hat{\eta}^2_G = .223\), 90\% CI \([.159, .282]\), \(\mathrm{BF}_{\textrm{10}} = 2.22 \times 10^{45}\)) and an interaction between \(n\)-back level and NFC scores (\(F(2.10, 239.56) = 4.93\), \(p = .007\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .025]\)), but no main effect of NFC scores (\(F(1, 114) = 3.22\), \(p = .075\), \(\hat{\eta}^2_G = .022\), 90\% CI \([.000, .084]\), \(\mathrm{BF}_{\textrm{10}} = 1.75 \times 10^{2}\)).
Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (\(t(114) = -2.15\), \(p = .033\), \(\mathrm{BF}_{\textrm{10}} = 11.15\)) and for 4-back (\(t(114) = -2.89\), \(p = .005\), \(\mathrm{BF}_{\textrm{10}} = 336.88\)) than those with NFC scores above the median, so evidence was in favour of H3b.
Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of \(n\)-back levels (Supplementary Figure S3).

With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of NFC group (\(F(1, 114) = 8.43\), \(p = .004\), \(\hat{\eta}^2_G = .043\), 90\% CI \([.003, .119]\), \(\mathrm{BF}_{\textrm{10}} = 14.26\)) and a main effect of the \(n\)-back level (\(F(1, 114) = 10.21\), \(p = .002\), \(\hat{\eta}^2_G = .034\), 90\% CI \([.000, .105]\), ), but no interaction (\(F(1, 114) = 2.59\), \(p = .110\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .058]\)).
In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (\(t(114) = 2.90\), \(p = .004\)) (Supplementary Figure S2b).
Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was more negative than that of 1- and 2-back (\(t(114) = 3.20\), \(p = .002\)), indicating that in the same way in which the SVs decreased more strongly from 2- to 3-back than from 1- to 2-back, the aversion increased more strongly.
The full results of these analyses of NFC group differences can be found in Table S.11 to S.15 in the Supplementary Material.

\hypertarget{exploratory-analyses}{%
\section{Exploratory analyses}\label{exploratory-analyses}}

To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher \(n\)-back levels, we computed an rmANOVA with the within-factor level (1 to 4) and the between-factor NFC group (below/above median).
There was no main effect of NFC group (\(F(1, 114) = 2.63\), \(p = .108\), \(\hat{\eta}^2_G = .007\), 90\% CI \([.000, .053]\), \(2.95 \times 10^{-1}\)), but a main effect of the \(n\)-back level (\(F(2.01, 229.39) = 67.39\), \(p < .001\), \(\hat{\eta}^2_G = .295\), 90\% CI \([.228, .354]\), \(2.70 \times 10^{30}\)) and an interaction (\(F(2.01, 229.39) = 3.24\), \(p = .041\), \(\hat{\eta}^2_G = .020\), 90\% CI \([.000, .044]\)).
Post-hoc tests for the main effect of level showed that SVs were lower for the more difficult \(n\)-back level in each paired contrast except for 1- versus 2-back.
Post-hoc tests for the interaction effect showed that the NFC groups only had a significant difference in SVs for 4-back, where participants below the NFC median had lower scores (\(\Delta M = 0.11\), 95\% CI \([0.01, 0.22]\), \(t(114) = 2.13\), \(p = .036\)).
Despite not reaching significance, 1-back was the only level in which participants with NFC scores above the median seemed to have lower SVs than those with scores below the median (\(\Delta M = -0.05\), 95\% CI \([-0.11, 0.01]\), \(t(114) = -1.50\), \(p = .136\)).
The full results of this exploratory analysis of NFC group differences can be found in Table S.16 and S.17 in the Supplementary Material.
Supplementary Figure S4 shows the SVs per \(n\)-back level for participants with NFC scores above and below the median.

Following a reviewer's recommendation, we also analyzed the association of SVs with NFC as a continuous variable.
We computed an rmANOVA with the \(n\)-back level as a within variable and the standardized NFC score as a covariate to predict SVs.
Both the NFC score (\(F(1, 114) = 4.34\), \(p = .039\), \(\hat{\eta}^2_G = .011\), 90\% CI \([.000, .063]\), \(\mathrm{BF}_{\textrm{10}} = 0.57\)) and the \(n\)-back level (\(F(2.02, 229.75) = 67.24\), \(p < .001\), \(\hat{\eta}^2_G = .295\), 90\% CI \([.228, .354]\), \(\mathrm{BF}_{\textrm{10}} = 2.70 \times 10^{30}\)) showed significant main effects, as well as a significant interaction (\(F(2.02, 229.75) = 3.78\), \(p = .024\), \(\hat{\eta}^2_G = .023\), 90\% CI \([.000, .049]\), \(\mathrm{BF}_{\textrm{10}} = 0.12\)).
Analyzing the estimated marginal means of the linear trends for each \(n\)-back level indicated a significant difference between the slopes of 1-back and 4-back (\(\Delta M = -0.09\), \(95\%\ \mathrm{CI}_\mathrm{\scriptsize Tukey(4)}\) \([-0.15, -0.02]\), \(t(456) = -3.22\), \(p_\mathrm{\scriptsize Tukey(4)} = .008\)), but not between any other two levels.
Plotting the predicted slopes shows that there is a negative association between the predicted SVs and the NFC scores for 1-back, but a positive association between the predicted SVs and the NFC scores for 4-back (Figure~\ref{fig:nfccont-sv}).
The full results of this exploratory analysis of NFC as a continuous covariate can be found in Table S.18 and S.19 in the Supplementary Material.

{[}FIGURE \ref{fig:nfccont-sv} HERE{]}

@@

Both \(d'\) and the median RT changed across \(n\)-back levels, indicating that there was an increase in objective task load.
The steepest decrease in \(d'\) between levels was from 2- to 3-back, resembling the declining logistic curve of the SVs.
Interestingly, the median RT increased from 2- to 3-back, but did not differ between 2- and 4-back.
Since feedback was given after each round, this pattern could be interpreted in such a way that participants tried to compensate their lower accuracy in 3-back by relying more on luck than on memory in 4-back and prioritized speed over accuracy.
Furthermore, several participants said that they perceived 3-back as more difficult than 4-back because they found it is easier to remember chunks of stimuli when \(n\) was an even number than when \(n\) was an odd number.
This would support the notion that the manipulation of task load in an \(n\)-back task is not strictly continuous.
And lastly, the fact that neither accuracy nor speed is an informative performance measure by itself has been observed before\textsuperscript{47} and both show different associations with various measures of intelligence\textsuperscript{4}, suggesting that they should always be reported as separate indices.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Kool2010}{}}%
\CSLLeftMargin{48. }%
\CSLRightInline{Kool, W., McGuire, J. T., Rosen, Z. B. \& Botvinick, M. M. \href{https://doi.org/10.1037/a0020198}{Decision making and the avoidance of cognitive demand.} \emph{Journal of Experimental Psychology: General} \textbf{139}, 665--682 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-Thomson2022}{}}%
\CSLLeftMargin{49. }%
\CSLRightInline{Thomson, K. S. \& Oppenheimer, D. M. \href{https://doi.org/10.1177/17456916211064896}{The {``}{E}ffort {E}lephant{''} in the room: {W}hat is effort, anyway?} \emph{Perspectives on Psychological Science} \textbf{17}, 1633--1652 (2022).}
